The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-05-26 paper/ms.tex
Constant flux in the line

>>>>

Another important issue is the \ly flux, in several systems correlation
between the \ly flux and properties such as the peak shift has been found
 (cites), in our study we don't find this correlation mainly because the flux remain 
 constant for all the rotational velocities and because the flux of the line
 is independent of the viewing angle. This last feature is shown in 
 Fig.\ref{fig:muhisto} when clearly is seen that the flux of the line
 does not change with the viewing angle $\theta$ as it does in systems with
 anisotropic \ly emission \citep{Zheng2013} and most recently in
  Outflow-Driven Cavities \citep{Behrens2014}.
